Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-10 article/article.tex
Commit 2024-09-10 13:11
Commit 2024-09-10 18:14

>>>>

{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-3}

\caption{Example of Colar constant of $1367\,\text{W}/\text{m}^{2}$. The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:unnamed-chunk-1}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{../images/P-example-day-4}

\caption{Example of Colar constant of $1367\,\text{W}/\text{m}^{2}$. The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:unnamed-chunk-2}
\end{figure}

\caption{Example of Colar constant of $1367\,\text{W}/\text{m}^{2}$. The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.}\label{fig:unnamed-chunk-3}
\end{figure}
